Alex is attending the first edition of Robotic World Championship of Table 
Tennis. 
A competition that have all of the matches having the same rules listed below:

\begin{itemize}
\tightlist
\item A match shall consist of the best of 7 games,
      i.e., the results of matches must be 4 games to $k$, 
      where $0 \leq k \leq 3$.
\item A game shall be won by the player first scoring 11 points unless both 
      players score 10 points, when the game shall be won by the first player 
      subsequently gaining a lead of 2 points.
      For example, a game can be won at scores like 11-5, 11-9 or 12-10, 
      but not 10-5 or 11-10.
\item After each 2 points have been scored the receiving player shall become 
      the serving player and so on until the end of the game, unless both 
      players score 10 points, when the sequences of serving and receiving 
      shall be the same but each player shall serve for only 1 point in turn. 
      That is, the servicing order of the first 20 points is 
      \verb+AABBAABBAABBAABBAABB+, and will be followed by \verb+ABABAB+$\ldots$
      if necessary.
\item The player serving first in a game shall receive first in the next game 
      of the match.
\end{itemize}

Experience tells that when two robots clashes into each other, 
the variances affecting their winning chances can be simplified to 
who's serving for the point. This is due to the performances of the 
robots are physically consistent and won't be affected mentally.

Alex have listed some of the possible matchups, simplified to the winning 
chance of each servicing point of the robots, for you. Now it is your job to 
help him calculate the winning chance of each match for them.
