There is a transparent tape. Its length is exact one meter ($10^9$ nanometers).
In this problem, all numbers are integers, and we use a number to denote 
a position on the tape. The number $p$ denote the position of the point
has a distance $p$ nanometers from the head of the tape.

Bob is a master dyer, so he can color the tape precisely in nanometer scale.
He colors two sectors $[p_1,q_1]$ and $[p_2,q_2]$ into red. 
The color of the tape within the range between $p_1$ and $q_1$ is red. 
The color of the tape within the range between $p_2$ and $q_2$ is also red. 
And the rest parts of the tape remain transparent. 

To verify Bob's skill, we ask Ben, the tape folding master, to help us.
Ben can fold the tape perfectly at any position. 
If Ben fold the tape at $x$, then the new position of a certain point $p$ 
will be one of the following cases.
\begin{itemize}
\tightlist
\item If $p=x$, then it becomes the new head of the tape, i.e, it becomes $0$.
\item If $p>x$, then it becomes $p-x$.
\item If $p<x$, then it becomes $x-p$. 
\end{itemize}
After Ben folds the tape, we measure the total length of the red part of the
new tape. 
If the red part has the expected length, then we will believe Bob and Ben
are both masters in their skills.
Obviously, the color of some position of the new tape is determined by the 
colors of the corresponding positions of the old tape. 
A position of the new tape is colored in red if one of the corresponding 
positions in the old tape is colored in red. 

Bob has already colored the tape, and Ben has proposed the positions to be
folded. 
Please write a program to compute the expected lengths colored in red.
